Recruiting Chapter

### 2021-06-08 text/manuscript_june_2021.Rmd
started full manuscript rmd

library(kableExtra)
library(tidyverse)
library(gridExtra)
```

@@

Research question 1 asks, how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities? This question can be answered by counting the number of visits to private high schools, which equivalent to calculating degree centrality for each university. In addition to scale, we are also interested in the relative scale of visits to private high schools. That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.  Appendix Figures X and X show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities. Figures X and X show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.

INSERT FIGURE X AND FIGURE X ABOUT HERE

@@

>>>>

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(scales)

knitr::opts_chunk$set(echo = F, message = F)

data_dir <- file.path('..', 'data')
tables_dir <- file.path('..', 'assets', 'tables')
figures_dir <- file.path('..', 'assets', 'figures')

univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
  arrange(desc(classification), rank)
events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))

pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
```

@@

Research question 1 asks, how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities? This question can be answered by counting the number of visits to private high schools, which equivalent to calculating degree centrality for each university. In addition to scale, we are also interested in the relative scale of visits to private high schools. That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.  Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities. Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.

INSERT FIGURE \@ref(fig:events-hs-count-pubu) AND FIGURE \@ref(fig:events-hs-count-privu) ABOUT HERE

@@

```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
```

```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
```

# Appendix

```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
```

```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
```
